Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-13 report/report.tex
Update todo
Include updated project specification
Use kth template

\documentclass[a4paper]{article}

@@

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling}

\author{Alexander Hjelm}

\date{\today}

\begin{document}
\maketitle

\section{Abstract}

This project assesses the feasibility of creating a 3D representation of OpenStreetMap (OSM) geodata with the inclusion of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

@@

@@

% TODO: Move section 3.3 to preface (Exclude entirely?)
% TODO: Read through Todor's recommended papers

% After response from Todor:
% TODO: Write section: Utility in real world applications

% After wednesday meeting with Chris
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Fix citations so they adhere to the same model
% TODO: Spell check
% TODO: Go over report one final time

@@

>>>>

\documentclass{kththesis}

\usepackage{blindtext} % This is just to get some nonsense text in this template, can be safely removed

\usepackage{csquotes} % Recommended by biblatex
\usepackage[style=numeric,sorting=none,backend=biber]{biblatex}
\addbibresource{references.bib} % The file containing our references, in BibTeX format

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling}
\alttitle{Detta är den svenska översättningen av titeln}
\author{Alexander Hjelm}
\email{osquar@kth.se}
\supervisor{Lotta Larsson}
\examiner{Lennart Bladgren}
\hostcompany{Företaget AB} % Remove this line if the project was not done at a host company
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}

@@

% Uncomment the next line to include cover generated at https://intra.kth.se/kth-cover?l=en
% \kthcover{kth-cover.pdf}

\begin{document}

% Frontmatter includes the titlepage, abstracts and table-of-contents
\frontmatter

\titlepage

\begin{abstract}
  This project assesses the feasibility of creating a 3D representation of OpenStreetMap (OSM) geodata with the inclusion of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

@@

  \blindtext
\end{abstract}

\begin{otherlanguage}{swedish}
  \begin{abstract}
    Träutensilierna i ett tryckeri äro ingalunda en oviktig faktor,
    för trevnadens, ordningens och ekonomiens upprätthållande, och
    dock är det icke sällan som sorgliga erfarenheter göras på grund
    af det oförstånd med hvilket kaster, formbräden och regaler
    tillverkas och försäljas Kaster som äro dåligt hopkomna och af
    otillräckligt.
  \end{abstract}
\end{otherlanguage}

\tableofcontents

% Mainmatter is where the actual contents of the thesis goes
\mainmatter

@@

% Wednesday:
% TODO: Apply KTH thesis format
% TODO: Bold research questions
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions
% TODO: Reduce long section headlines
% TODO: Rename analysis -> conclusions
% TODO: Shorten abstract
% TODO: Verify that citings look correct (compare to other reports)

% Thursday:
% TODO: Abstract: Mention that the scientific study is a contribution
% TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
% TODO: Introduction (See meeting log for suggestions)
% TODO: Introduction, picture of a virtual city

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels)
% TODO: Read through Todor's recommended papers
% TODO: Scientific study, show how my work integrates in the 3D city reconstruction process.
    % TODO: A lot of the metrics I've used applyg for building accuracy as well (Fan)
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

% After wednesday meeting with Chris
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Spell check
% TODO: Go over report one final time

@@

\appendix

% Tailmatter inserts the back cover page (if enabled)
\tailmatter
